### 2018-08-08 paper/spor.tex
small error

Using $\theta$, \name becomes more conservative than \SPOR, and we can investigate the best number of nodes per layer in regard of its probability of being available.

>>>>

Using $\theta$, \name becomes more conservative than \ac{SPOR}, and we can investigate the best number of nodes per layer in regard of its probability of being available.
